Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-05-21 Chapter-6/6-PionCrossSection.tex
s

\subsection{Treatment of Systematics} \label{ch:SysUncertaintyXSRaw}
The only systematic effect considered in the measurement of the raw cross section results from the propagation of the uncertainty associate with the measurement of the kinetic energy at each slab.

>>>>

\subsection{Treatment of Systematics} \label{ch:SysUncertaintyXSRaw}
The only systematic effect considered in the measurement of the raw cross section results from the propagation of the uncertainty associate with the measurement of the kinetic energy at each argon slab. As shown in Section \ref{ch:kinEn}, the uncertainty on the kinetic energy of a pion candidate at the j$^{th}$ slab of argon  is given by

\begin{eqnarray}
\delta KE_{j} &=& \sqrt{\delta p_{Beam}^2 + \delta E_{Loss}^2 +  \delta  E_{\text{dep FF-j}}^2},\\
&=& \sqrt{(2\% \text{ }p_{Beam})^2 +  (\sim 7 \text{ [MeV]})^2 +  (j-1)^2 (\sim0.08\text{ [MeV]})^2}.
\end{eqnarray}

We propagate this uncertainty  by varying the energy measurement $KE_{j}$ at each argon slab. We calculating the $N^{\text{TOT}}_{\text{Inc}}$,  $N^{\text{TOT}}_{\text{Int}}$ and cross section plots in three cases: first assigning the measured $KE_{j}$ at each kinetic energy sampling, then assigning $KE_{j} + \delta KE_{j}$, and finally assigning $KE_{j} - \delta KE_{j}$. The difference between the values obtained using the $KE_{j}$ sampling and the maximum and minimum values in each kinetic energy bin determines the systematic uncertainty.

%We propagate this uncertainty  by calculating the $N^{\text{TOT}}_{\text{Inc}}$,  $N^{\text{TOT}}_{\text{Int}}$ and cross section plots twice: first assigning $KE_{j} + \delta KE_{j}$ at each kinetic energy sampling, then assigning $KE_{j} - \delta KE_{j}$. The difference between the central value and the maximum and minimum value in each kinetic energy bin gives the systematic uncertainty.
